---
title: "workspace"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{workspace}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
# load_all()
```

* Tune knn imputation with hyper parameters
* Possibly use the same thing for missMDA imput PCA
* Tune by specific chromosome and group

for each combination of hyper parameter
  for each group
    for each chromosome
      for each replication
        inject NA (inject_na)
        impute (results)
        calculate and return prediction error 
      average result across replication
      return chromosome and group wise best combination of hyper parameter

```{r}
# s <- sim_mat(10000, 30, perc_col_NA = 0.5)
# tune_prep(X = s$input, ampute = FALSE, temp_path = NA)
# a <- tune_knn(
#   X = s$input,
#   group_sample = s$group_sample,
#   group_feature = s$group_feature,
#   hp = data.frame(k = 1, maxp_prop = 0.1),
#   min_na = 1,
#   max_na = 10
# )
# 
# b <- fit_imputePCA(
#   X = s$input,
#   # group_sample = s$group_sample,
#   # group_feature = s$group_feature,
#   hp = data.frame(ncp = 1)
# )
# 
# b |> dim()
```

