---
title: "workspace"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{workspace}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
# load_all()
```

* Tune knn imputation with hyper parameters
* Possibly use the same thing for missMDA imput PCA
* Tune by specific chromosome and group

for each combination of hyper parameter
  for each group
    for each chromosome
      for each replication
        inject NA (inject_na)
        impute (results)
        calculate and return prediction error 
      average result across replication
      return chromosome and group wise best combination of hyper parameter

```{r}
# s <- sim_mat(100, 10)
#
# set.seed(1234)
# inject_na(
#   s$input,
#   feature_id = s$group_feature$feature_id,
#   sample_id = s$group_sample$sample_id, prop = 0.05,
#   c_thresh = 1,
#   r_thresh = 1
# )
#
# a <- tune_knn(
#   X = s$input,
#   hp = data.frame(k = c(1, 2), maxp_prop = c(0.5, 0.7)),
#   group_sample = s$group_sample,
#   group_feature = s$group_feature,
#   rep = 2,
#   prop = c(0.1)
# )
#
# b <- tune_imputePCA(
#   X = s$input,
#   hp = data.frame(ncp = 1),
#   group_sample = s$group_sample,
#   group_feature = s$group_feature,
#   rep = 2,
#   prop = c(0.1)
# )
#
# a$r_names
# b$r_names
```

